---
title: "Mini Data-Analysis Deliverable 1"
output: github_document
---

```{r include = FALSE}
knitr::opts_chunk$set(error = TRUE)
```

# Welcome to your (maybe) first-ever data analysis project!

And hopefully the first of many. Let's get started:

1.  Install the [`datateachr`](https://github.com/UBC-MDS/datateachr) package by typing the following into your **R terminal**:

<!-- -->

    install.packages("devtools")
    devtools::install_github("UBC-MDS/datateachr")

2.  Load the packages below.

```{r}
library(datateachr)
library(tidyverse)
```

3.  Make a repository in the <https://github.com/stat545ubc-2022> Organization. You will be working with this repository for the entire data analysis project. You can either make it public, or make it private and add the TA's and Lucy as collaborators. A link to help you create a private repository is available on the #collaborative-project Slack channel. 

# Instructions

## For Both Milestones

-   Each milestone is worth 45 points. The number of points allocated to each task will be annotated within each deliverable. Tasks that are more challenging will often be allocated more points.

-   10 points will be allocated to the reproducibility, cleanliness, and coherence of the overall analysis. While the two milestones will be submitted as independent deliverables, the analysis itself is a continuum - think of it as two chapters to a story. Each chapter, or in this case, portion of your analysis, should be easily followed through by someone unfamiliar with the content. [Here](https://swcarpentry.github.io/r-novice-inflammation/06-best-practices-R/) is a good resource for what constitutes "good code". Learning good coding practices early in your career will save you hassle later on!

## For Milestone 1

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-1.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work below --->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to the mini-analysis GitHub repository you made earlier, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 45 points: 43 for your analysis, 1 point for having your Milestone 1 document knit error-free, and 1 point for tagging your release on Github.

# Learning Objectives

By the end of this milestone, you should:

-   Become familiar with your dataset of choosing
-   Select 4 questions that you would like to answer with your data
-   Generate a reproducible and clear report using R Markdown
-   Become familiar with manipulating and summarizing your data in tibbles using `dplyr`, with a research question in mind.

# Task 1: Choose your favorite dataset (10 points)

The `datateachr` package by Hayley Boyce and Jordan Bourak currently composed of 7 semi-tidy datasets for educational purposes. Here is a brief description of each dataset:

-   *apt_buildings*: Acquired courtesy of The City of Toronto's Open Data Portal. It currently has 3455 rows and 37 columns.

-   *building_permits*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 20680 rows and 14 columns.

-   *cancer_sample*: Acquired courtesy of UCI Machine Learning Repository. It currently has 569 rows and 32 columns.

-   *flow_sample*: Acquired courtesy of The Government of Canada's Historical Hydrometric Database. It currently has 218 rows and 7 columns.

-   *parking_meters*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 10032 rows and 22 columns.

-   *steam_games*: Acquired courtesy of Kaggle. It currently has 40833 rows and 21 columns.

-   *vancouver_trees*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 146611 rows and 20 columns.

**Things to keep in mind**

-   We hope that this project will serve as practice for carrying our your own *independent* data analysis. Remember to comment your code, be explicit about what you are doing, and write notes in this markdown document when you feel that context is required. As you advance in the project, prompts and hints to do this will be diminished - it'll be up to you!

-   Before choosing a dataset, you should always keep in mind **your goal**, or in other ways, *what you wish to achieve with this data*. This mini data-analysis project focuses on *data wrangling*, *tidying*, and *visualization*. In short, it's a way for you to get your feet wet with exploring data on your own.

And that is exactly the first thing that you will do!

1.1 Out of the 7 datasets available in the `datateachr` package, choose **4** that appeal to you based on their description. Write your choices below:

**Note**: We encourage you to use the ones in the `datateachr` package, but if you have a dataset that you'd really like to use, you can include it here. But, please check with a member of the teaching team to see whether the dataset is of appropriate complexity. Also, include a **brief** description of the dataset here to help the teaching team understand your data.

<!-------------------------- Start your work below ---------------------------->
## **<span style ="color: purple;">My 4 Potential DataSet Choices</span>**
1. cancer_sample
2. vancouver_trees
3. steam_games
4. parking_meters
<!----------------------------------------------------------------------------->

1.2 One way to narrowing down your selection is to *explore* the datasets. Use your knowledge of dplyr to find out at least *3* attributes about each of these datasets (an attribute is something such as number of rows, variables, class type...). The goal here is to have an idea of *what the data looks like*.

*Hint:* This is one of those times when you should think about the cleanliness of your analysis. I added a single code chunk for you below, but do you want to use more than one? Would you like to write more comments outside of the code chunk?

<!-------------------------- Start your work below ---------------------------->
## **<span style ="color: purple;">Determining the attributes of my potential datasets</span>**
The 4 code chunks below explore the attributes of my 4 potential datasets. The 4 attributes investigated are the following: class, number of observations (rows), number of variables (columns), names of all variables. To finish this exploration, the first 5 rows of each dataset will be displayed!

**The code below explores the attributes of the <span style ="color: blue;">*cancer_sample*</span> dataset.** 
Based on the results below, the cancer_sample dataset is a tibble with 569 rows and 32 columns. These columns (variables) are of the following types: character & double-precision floating point number.
```{r}
class(cancer_sample)
dim(cancer_sample)
glimpse(cancer_sample, 5)
```

**The code below explores the attributes of the <span style ="color: blue;">*vancouver_trees*</span> dataset.**
Based on the results below, the vancouver_trees dataset is a tibble with 146,611 rows and 22 columns. These columns (variables) are of the following types: character, double-precision floating point number & date.
```{r}
class(vancouver_trees)
dim(vancouver_trees)
glimpse(vancouver_trees, 5)
```

**The code below explores the attributes of the <span style ="color: blue;">*steam_games*</span> dataset.**
Based on the results below, the vancouver_trees dataset is a tibble with 40,833 rows and 21 columns. These columns (variables) are of the following types: character & double-precision floating point number.
```{r}
class(steam_games)
dim(steam_games)
glimpse(steam_games, 5)
```

**The code below explores the attributes of the <span style ="color: blue;">*parking_meters*</span> dataset.**
Based on the results below, the vancouver_trees dataset is a tibble with 10032 rows and 22 columns. These columns (variables) are of the following types: character & double-precision floating point number.
```{r}
class(parking_meters)
dim(parking_meters)
glimpse(parking_meters, 5)
```

<!----------------------------------------------------------------------------->

1.3 Now that you've explored the 4 datasets that you were initially most interested in, let's narrow it down to 2. What lead you to choose these 2? Briefly explain your choices below, and feel free to include any code in your explanation.

<!-------------------------- Start your work below ---------------------------->
## **<span style ="color: purple;">Narrowing it down to 2 datasets</span>**

After giving it much thought, I have narrowed my options down to the following 2 datasets:

1. **<span style ="color: blue;">cancer_sample:</span>** I have chosen this dataset purely out of interest and relevance. I am a graduate student in the Department of Microbiology & Immunology and my supervisor's lab is based at BCCHR. As such, my graduate thesis project is heavily reliant on the ability to work with and manipulate healthcare data. For this reason, I believe that the cancer_sample dataset is most similar to the datasets I will be working on in the future, and, thus, a good dataset for me to 'get my feet wet'!

2. **<span style ="color: blue;">vancouver_trees:</span>** I chose this dataset because it has the greatest number of observations(rows) out of the 7 given datasets. Datasets with a large number of observations(rows) are generally preferred for statistical analysis because they usually have a higher statistical power and, thus, better predictive capabilities. I also find this dataset very interesting because it'll allow me to explore topics that I normally wouldn't have the time/opportunity to investigate.
<!----------------------------------------------------------------------------->

1.4 Time for the final decision! Going back to the beginning, it's important to have an *end goal* in mind. For example, if I had chosen the `titanic` dataset for my project, I might've wanted to explore the relationship between survival and other variables. Try to think of 1 research question that you would want to answer with each dataset. Note them down below, and make your final choice based on what seems more interesting to you!

<!-------------------------- Start your work below ---------------------------->
## **<span style ="color: purple;">Final Decision Regarding Which DataSet To Explore Further</span>**

In an attempt to decide on a dataset between the 2 listed previously, I have chosen 1 research question for each dataset. The research questions are as follows:

1. **<span style ="color: blue;">cancer_sample:</span>** Do cell nuclei classified as malignant have a greater, smaller, or equal radius compared to those classified as benign?
2. **<span style ="color: blue;">vancouver_trees:</span>** On average, during which month of the year are the most trees planted in Vancouver?

<span style="color: limegreen;">**Based on the questions listed above, I have decided to explore the *vancouver_trees* dataset further.**</span>
<!----------------------------------------------------------------------------->

# Important note

Read Tasks 2 and 3 *fully* before starting to complete either of them. Probably also a good point to grab a coffee to get ready for the fun part!

This project is semi-guided, but meant to be *independent*. For this reason, you will complete tasks 2 and 3 below (under the **START HERE** mark) as if you were writing your own exploratory data analysis report, and this guidance never existed! Feel free to add a brief introduction section to your project, format the document with markdown syntax as you deem appropriate, and structure the analysis as you deem appropriate. Remember, marks will be awarded for completion of the 4 tasks, but 10 points of the whole project are allocated to a reproducible and clean analysis. If you feel lost, you can find a sample data analysis [here](https://www.kaggle.com/headsortails/tidy-titarnic) to have a better idea. However, bear in mind that it is **just an example** and you will not be required to have that level of complexity in your project.

# Task 2: Exploring your dataset (15 points)

If we rewind and go back to the learning objectives, you'll see that by the end of this deliverable, you should have formulated *4* research questions about your data that you may want to answer during your project. However, it may be handy to do some more exploration on your dataset of choice before creating these questions - by looking at the data, you may get more ideas. **Before you start this task, read all instructions carefully until you reach START HERE under Task 3**.

2.1 Complete *4 out of the following 8 exercises* to dive deeper into your data. All datasets are different and therefore, not all of these tasks may make sense for your data - which is why you should only answer *4*. Use *dplyr* and *ggplot*.

1.  Plot the distribution of a numeric variable.
2.  Create a new variable based on other variables in your data (only if it makes sense)
3.  Investigate how many missing values there are per variable. Can you find a way to plot this?
4.  Explore the relationship between 2 variables in a plot.
5.  Filter observations in your data according to your own criteria. Think of what you'd like to explore - again, if this was the `titanic` dataset, I may want to narrow my search down to passengers born in a particular year...
6.  Use a boxplot to look at the frequency of different observations within a single variable. You can do this for more than one variable if you wish!
7.  Make a new tibble with a subset of your data, with variables and observations that you are interested in exploring.
8.  Use a density plot to explore any of your variables (that are suitable for this type of plot).

2.2 For each of the 4 exercises that you complete, provide a *brief explanation* of why you chose that exercise in relation to your data (in other words, why does it make sense to do that?), and sufficient comments for a reader to understand your reasoning and code.

<!-------------------------- Start your work below ---------------------------->
## **<span style ="color: purple;">Exploring the Dataset</span>**

In order to get a better understanding of this dataset, I have completed 4 different exercises below using *dplyr* and *ggplot*.

### **<span style ="color: deeppink;">Exercise 1: Investigate the number of missing values per variable and plot it</span>**

To begin this exploration of the *vancouver_trees* dataset, I will start by determining which variables have the greatest number of missing values. This will be helpful in future analyses, as it will allow me to interpret trends/patterns associated with these variables with caution.

First off, missing values in this dataset are indicated by blank cells. I will start by converting these cells to NA in order to be able to count the number of NA's in the subsequent steps. I will also print a summary of the dataset to ensure that there are NA's present in the dataset following the aforementioned manipulations.
```{r}
vancouver_trees <- vancouver_trees %>%
  na_if(y = "")
summary(vancouver_trees)
```
Next, I will count the number of NA's for each variable and plot this information on a bar plot, with the x-axis labeled 'Name of Variable' and the y-axis being labeled 'Number of Missing Values'.
```{r}
count_NA <- vancouver_trees %>%
  summarise(across(c(everything(),-tree_id,-civic_number), ~ sum(is.na(.))))

count_NA_long <- count_NA %>%
  pivot_longer(std_street:latitude)

count_NA_long %>%
  ggplot(aes(x = name, y = value)) +
  geom_col(color = "hotpink4", fill = "hotpink1") +
  labs(x = "Name of Variable", y = "Number of Missing Values") +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  theme_classic()
```

### **<span style ="color: deeppink;">Exercise 2: Plot the distribution of a numeric variable</span>**

For this exercise, I intend to plot the distribution of the *height_range_id* of trees in Vancouver. I have created a histogram which has 'Height Range of Tree (x10 ft)' on the x-axis and 'Count' on the y-axis.
```{r}
vancouver_trees%>%
  ggplot(mapping = aes(height_range_id)) +
  geom_bar(alpha=0.7, color="hotpink4", fill = "hotpink1") +
  labs(x = "Height Range of Tree (x10 ft)", y = "Count")
```

### **<span style ="color: deeppink;">Exercise 3: Create a new variable based on other variables in your data (only if it makes sense)</span>**
The vancouver_trees dataset contains a variable named *height_range_ID*. This variable is stored as a numeric variable; however, in reality, it represents different categories into which the trees are placed. For example, a height_range_id of 5 means that the height of the tree is anywhere from 50-60 feet. On the lower end, a height_range_id of 0 means that the height of the tree is anywhere from 0-10 feet. On the other extreme, a height_range_id of 10 means that the height of the tree is greater than 100 feet. As a result, I will be converting this numerical variable into a factor with the levels being 0-10, 10-20, 20-30, and so on. At the end, I use the levels() function to ensure that this worked!

This will result in the creation of the vancouver_trees_height_factor dataset, which is a modified form of vancouver_trees. It has all blank values replaced with NA, and a new column has been created called 'height' which is a factor with the levels previously described.

```{r}
vancouver_trees_height_factor <- vancouver_trees %>%
  mutate('height' = as.factor(height_range_id))
height_factors <- c('0' = "0-10", '1' = "10-20", '2' = "20-30", '3' = "30-40", '4' = "40-50", '5' = "50-60", '6' = "60-70", '7' = "70-80", '8' = "80-90", '9' = "90-100", '10' = "Above 100")
vancouver_trees_height_factor$height <- recode_factor(vancouver_trees_height_factor$height, !!!height_factors, .ordered = TRUE)
levels(vancouver_trees_height_factor$height)
```

### **<span style ="color: deeppink;">Exercise 3: Make a new tibble with a subset of your data, with variables and observations that you are interested in exploring</span>**

For this exercise, I will create a new tibble, which will contain a subset of my data, more specifically the variables that I consider to be potentially relevant for my 4 research questions. Lastly, I will print the tibble to ensure that it has the correct number of columns and was subsetted correctly!
```{r}
irrelevant_variables <- c("tree_id","civic_number","assigned","longitude","latitude")

vancouver_trees_data <- vancouver_trees %>%
  select(everything(),-irrelevant_variables)

print(vancouver_trees_data)
```

<!--- *****START HERE***** --->
## **<span style ="color: purple;">My 4 Research Questions</span>**

My 4 potential research questions for the <span style ="color: blue;">*vancouver_trees*</span> dataset are as follows:

1. What is the most common diameter for trees in Vancouver?
2. Which genus of trees in Vancouver has the greatest diameter?
3. Is there a linear relationship between the height and diameter of trees?
4. Which neighborhood in Vancouver has the greatest biodiversity?

# Task 4: Process and summarize your data (13 points)

From Task 2, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions.

### 1.1 (10 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*
4.  Based on two categorical variables, calculate two summary statistics of your choosing.

**Graphing:**

5.  Create a graph out of summarized variables that has at least two geom layers.
6.  Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7.  Make a graph where it makes sense to customize the alpha transparency.
8.  Create 3 histograms out of summarized variables, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->
## **<span style ="color: purple;">Processing and Summarizing Data</span>**

### **<span style ="color: deeppink;">Research Question # 1: What is the most common diameter for trees in Vancouver?</span>**
#### **<span style ="color: orange;">Summarizing Task</span>**
For this section, I have chosen summarizing task # 1, as described above. The numerical variable I will be using will be the *diameter* of the trees at breast height (in). I will be calculating its range, mean, standard deviation, and interquartile range for each genus of trees. 
```{r}
vancouver_trees %>%
  group_by(genus_name) %>%
  summarize(range_diameter = max(diameter)-min(diameter), mean_diameter = mean(diameter), sd_diameter = sd(diameter), IQR_diameter = IQR(diameter))
```
#### **<span style ="color: orange;">Graphing Task</span>**
For this task, I have plotted the distribution of the diameter (inches) of trees in Vancouver on a histogram with 'Diameter of Tree at Breast Height (in)' on the x-axis and 'Count' on the y-axis. This graph was created to satisfy the requirements of graphing task #8. As such, 3 histograms with different bin widths are shown below. For the first histogram, the bin width was set to be 100, followed by a bin width of 5 for the second histogram. The bin width of the last histogram was chosen using the Freedman-Diaconis rule, which advises on the optimal bin width for a given graph based on the interquartile range and the number of observations through an equation. In my opinion, the second histogram has the best bin width. This is because the bins aren't too big that all observations fall into one bin (this is the case with the first histogram), and the bins aren't too small either which would make it difficult to distinguish between the different bins (this is the case with the third histogram). Simply by looking at the second histogram, we can tell that most values for the diameter of trees in Vancouver fall between 5-20 inches.
```{r}
vancouver_trees %>%
  ggplot(mapping = aes(diameter)) +
  geom_histogram(binwidth = 100, color="chartreuse4", fill = "chartreuse4") +
  labs(x = "Diameter of Tree at Breast Height (in)", y = "Count") +
  theme_classic()
```
```{r}
vancouver_trees %>%
  ggplot(mapping = aes(diameter)) +
  geom_histogram(binwidth=5, color="chartreuse4", fill = "chartreuse4") +
  labs(x = "Diameter of Tree at Breast Height (in)", y = "Count") +
  theme_classic()
```
```{r}
optimal_bin_width <- ((IQR(vancouver_trees$diameter))*2)/(length(vancouver_trees$diameter)^(1/3))

vancouver_trees %>%
  ggplot(mapping = aes(diameter)) +
  geom_histogram(binwidth=optimal_bin_width, color="chartreuse4", fill = "chartreuse4") +
  labs(x = "Diameter of Tree at Breast Height (in)", y = "Count") +
  theme_classic()
```

### **<span style ="color: deeppink;">Research Question # 2: Which genus of trees in Vancouver has the greatest diameter?</span>**
#### **<span style ="color: orange;">Summarizing Task:</span>**
For this research question, I have chosen summarizing task # 2. As per the instructions, I have computed the number of observations (rows) for the categorical variable *genus_name* below. I have sliced the dataset to keep only the top 5 most prevalent genera in Vancouver. The reasoning for this will become apparent in the corresponding graphing task.
```{r}
vancouver_trees_top5 <- vancouver_trees %>%
  group_by(genus_name) %>%
  summarise(n=n()) %>%
  arrange(desc(n)) %>%
  slice(1:5)

print(vancouver_trees_top5)
```
#### **<span style ="color: orange;">Graphing Task:</span>**
I will be completing graphing task # 7, which requires the use of alpha transparency. Below, I have created a density plot which shows the distribution of the numeric variable *diameter* according to *genus_name*. Given that this dataset has a wide array of genera, I will be looking only at the top 5 genera of trees that are most prevalent in Vancouver. Additionally, based on previous analyses, I know that the range of *diameter* is quite long. Due to this, I will limit the range of my x-axis to 0-50 feet.
```{r}
vancouver_trees %>%
  filter(genus_name %in% vancouver_trees_top5$genus_name) %>%
  ggplot(mapping = aes(x = diameter, group = genus_name, fill = genus_name)) +
  geom_density(alpha=0.5) +
  labs(x = "Diameter of Tree at Breast Height (in)", y = "Density") +
  xlim(0,50) +
  theme_linedraw()
```


### **<span style ="color: deeppink;">Research Question # 3: Is there a linear relationship between the height and diameter of trees?</span>**
#### **<span style ="color: orange;">Summarizing Task</span>**
For this question, I have chosen summarizing task # 1, as described above. Previously, I have calculated the range, mean, interquartile range, and standard deviation of the diameter of trees belonging to a given genus. However, I have not calculated this statistical information for the height these trees. Below, I will calculate the mean and range for height, alongside the standard deviation and interquartile range, in order to be able to adequately compare height and diameter in answering my research question.
```{r}
vancouver_trees %>%
  group_by(genus_name) %>%
  summarize(range_height_range_id = max(height_range_id)-min(height_range_id), mean_height_range_id = mean(height_range_id), sd_height_range_id = sd(height_range_id), IQR_height_range_id = IQR(height_range_id))
```
#### **<span style ="color: orange;">Graphing Task</span>**
For the graphing task for research question # 3, I will be completing task # 5.
```{r}
ggplot(vancouver_trees, aes(x=diameter, y=height_range_id)) +
geom_point(size = 0.009, color="black") +
  geom_smooth(linetype="dashed", color="goldenrod3") +
  labs(x = "Diameter of Tree at Breast Height (in)", y = "Height Range (0-10)")+
  theme_linedraw()
```

### **<span style ="color: deeppink;">Research Question # 4: Which neighborhood in Vancouver has the greatest biodiversity?</span>**

#### **<span style ="color: orange;">Summarizing Task:</span>**
For this task, I have decided to complete summarizing task # 2. As such, I have computed the number of observations for the categorical variable *neighborhood_name* below!

```{r}
vancouver_trees_data_neighborhood <- vancouver_trees %>%
  group_by(neighbourhood_name) %>%
  summarize(n=n())
print(vancouver_trees_data_neighborhood)
```

```{r}
vancouver_trees_data_neighborhood <- vancouver_trees%>%
  group_by(neighbourhood_name) %>%
  filter(neighbourhood_name %in% vancouver_trees_data_neighborhood$neighbourhood_name) %>%
  summarise(n=n(), n_species = n_distinct(species_name))

print(vancouver_trees_data_neighborhood)
```
#### **<span style ="color: orange;">Graphing Task:</span>**
For this graphing task, I have chosen to complete task # 5. As per the instructions, I have plotted two geom layers (geom_col and geom_line) on the same plot. The line graph represents the # of distinct species of trees in each given neighborhood. This will aid me in answering my research question, because the amount of biodiversity in a particular neighborhood is dependent on the total number of trees as well as the total number of distinct tree species.
```{r}
vancouver_trees_data_neighborhood %>%
  ggplot(aes(x = neighbourhood_name, group = 1)) +
  geom_col(aes(y = n), color="coral1", fill="coral", alpha=0.5) +
  geom_line(aes(y= n_species*10)) +
  labs(x = "Name of Neighborhood", y = "Number of Trees") +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  theme(axis.text.x = element_text(size=6))
```

<!----------------------------------------------------------------------------->

### 1.2 (3 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

<!-------------------------- Start your work below ---------------------------->
## **<span style ="color: purple;">Conclusion</span>**

Based on the operations I have completed, I do believe that I'm significantly closer to answering my research questions. One aspect that does remain unclear, however, is the relationship between the height of a given tree and its diameter (as discussed in research question # 3). This is because the heights of the trees are given as a range from 0-10, with integers being the only possibility. As a result, some information in lost when storing data in this manner. For example, trees that would've had a height of 56 ft would be stored as 5, and those with a height of 32 feet would be stored as 3. This would influence the power and overall statistical significance of my results, making it much more difficult to view trends. This is particularly why I believe that the graph produced for this research question has such an interesting shape!
<!----------------------------------------------------------------------------->

### Attribution

Thanks to Icíar Fernández Boyano for mostly putting this together, and Vincenzo Coia for launching.
